### 2019-02-13 sections/relatedwork.tex

That being said, there are some concepts that are similar in \TOP and FRP.
The \emph{stepper} behavior for example is associated with an event and yields the value of the most recent event.
This is similar to editors in \TOP.
Furthermore, both systems can be used to declaratively program user interfaces.

>>>>

That being said, there are some concepts that are similar in \TOP and FRP.
The \emph{stepper} behavior for example is associated with an event and yields the value of the most recent event.
This is similar to editors in \TOP.
Furthermore, both systems can be used to declaratively program user interfaces, albeit in FRP the programmer has to construct the GUI elements manually, and connect inputs and outputs to the correct events and behaviors.
In \TOP graphical user interfaces are automatically derived.
